|

### 2021-05-27 article/resubmission.Rmd
adds results 1st draft

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity. Most
early studies that empirically tested the "law of $1/n$", as the theory is
currently known, indeed found a positive correlation between the number of
legislature seats and different measures of government spending, although the
effect was often limited to one house [e.g., @baqir2002districting;
@gilligan1995deviations; @gilligan2001fiscal]. Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
collection of small districts can supply public goods more efficiently than the
central government. The authors conclude that a "reverse law of $1/n$" may hold,
wherein a higher number of legislators in small constituencies decrease the
overall public spending. Recent research has further
questioned the validity of the "law of $1/n$". Since the wide range of empirical tests has produced conflicting results, scholars began to target the theoretical foundations of the law. Authors such as @crowley2019law and @pecorino2018supermajority accurately point out that collective action problems have been overlooked, but their expanded models cannot account for all the institutional variation previous studies explore.

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We select `r length(unique(dat$id))` articles that
use quantitative methods to assess the impact of legislature size over
government spending across several dimensions. Out 
of the `r dim(dat)[1]` coefficients
included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
negative and statistically significant. Although other studies aimed at solving this inconsistency, meta-analysis is the most appropriate tool, as it combines multiple outcomes into a single estimation and allows
us to draw robust conclusions from the aggregated data [@cooper2019handbook; @hedges1985statistical]. It can also identify potential
sources of study heterogeneity, enabling researchers to assess threats to
external validity and direct future efforts into more promising areas of
academic inquiry [@doucouliagos2008democracy].

We believe the scrutiny of the law expanded its initial scope in two directions. One group of scholars investigates the original institutional framework for the presence of coalitions, supermajorities, veto powers, and spending limits, which the theory disregards. They suggest these dynamics strongly influence the $1/n$ effect -- specifically in U.S. majoritarian local legislatures, for which the law was conceived. Another sector of the scholarship overrides this institutional context. They find that the different political arrangements in national congresses, State legislatures, regional European governments, etc. produce more nuanced results. For instance, intergovernmental competition, the size ratio between assemblies, and strong executives demonstrated the effect of legislative size on public spending could be non-linear, asymmetrical, and even negative. While these trends evolved, causal inference tools became more sophisticated, allowing this inquiry to grow also in roubstness. We address all of these developments in this study. We coded five different moderators that translate methodological advances in time, the similarity of the empirical cases to the original @weingast1981political framework, and key theoretical issues to identify sources of variation in the literature.

Aggregate results show that legislative size has no significant impact on
public spending. Our meta-analysis estimates are exactly half positive, and half negative. 
Meta-regressions suggest that our study sample is highly heterogeneous, and effects differ substantially according to study specifications. In the broadest aggregation models, unicameralism supports the positive effect predicted by the 
law of $1/n$. Since most unicameral cases in our sample refer to local governments (municipalities or districts), this result supports the theory strictly in its original institutional framework. It also indirectly endorses studies that find odd results in bicameralism. As follows, meta-regressions confirm previous findings that larger upper chambers spend more in terms of per capita expenditure than lower chambers [@gilligan1995deviations; @gilligan2001fiscal]. 
Moreover, non-majoritarian voting systems decrease government spending as a percentage of GDP, and they do not have a relevant impact on the other measures of public expenditure, following the idea that the $1/n$ effect grows weaker as the empirical cases distance from the original formulation of the law.

The meta-regressions also indicate that the $1/n$ effect found in earlier studies might be sensitive to more robust estimation methods. While papers that employ conventional linear regressions often find a positive relation between
legislature size and government budgets, recent studies using modern methods of
causal inference, specially those with regression discontinuity designs,
provide consistent evidence for a negative relation [@crowley2019law; @debenedetto2018; @hohmann2017effect; @lewis2019legislature]. This goes in contrast with
the original theory and supports the existence of a "reverse law of $1/n$". In summary, our results are in line 
with previous findings that lend partial support to the law of $1/n$ 
[@chen2007law; @crowley2015local; @primo2006stop]. An assessment of the effects of collective action costs in these analyses is crucial to determine the full mechanism operating behind these results. Overall, our analysis does not
provide robust support for the theory as originally conceived.

# Methods

We compiled our study sample in three rounds. In the first search round, we
gathered data from three large academic databases (Scopus, Microsoft Academic,
and Google Scholar) and looked for studies that cited
\citet{weingast1981political}, as it is the foundational work in the literature
on the "law of $1/n$". We then restricted our query to articles written in
English and, to ensure that studies were comparable, we only included papers
that used quantitative methods to investigate the relationship between
legislature size and public spending\footnote{Please refer to Section C in the
Supplementary Material for a detailed description of the selection procedure.
We include two PRISMA (Preferred Reporting Items for Systematic Reviews and
Meta-Analyses) flow diagrammes \citep{liberati2009prisma} showing the number of
resulting papers after each review step.}. After this stage, we identified the
variables authors most commonly employ to measure government expenditure and
legislature size, our dependent and independent variables, respectively. For
government expenditure, our study sample uses (i) public expenditure as a share
of GDP; (ii) public expenditure per capita; and (iii) the natural logarithm of
public expenditure per capita as its main variables of interest\footnote{Since
meta-analysis requires a single estimate per observation, we excluded articles
that use interaction terms or quadratic specifications of our selected
variables.}. In regards to legislature size, the variables are (i) lower
chamber size; (ii) natural logarithm of lower chamber size; and (iii) upper
house size\footnote{There are a few important nuances concerning coding of
these variables. For instance, unicameralism is captured both by lower chamber
size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of the
literature estimates how institutional designs affect this relationship, ours
and many other articles use both lower and upper chamber sizes as main
explanatory variables. We did not find any articles that used the natural
logarithm of upper chamber size.}.

In the second round, we did not require articles to cite @weingast1981political
and used a keyword-based query on Google Scholar to broaden the scope of the
first search. We again restricted the search to articles written in English
which employed quantitative methods. In the third search round, we looked into
the personal webpages of every author we had already included in our previous
sample. The purpose of this manual search was to assess whether there was any
working paper or unpublished manuscript which we might had missed in the
previous queries. All papers we found in that last search had already been
included in our sample. Combined, the three searches produced a dataset of 
`r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March,
2021. Table \ref{tab:papers} contains the full list of articles we analyse in
this paper.

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead 
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Notre:} Country codes
follow the ISO 3166-1 alpha-3 international standard.}
\footnotetext{\textbf{Journals:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
\footnotetext{\textbf{Methods:} 
OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
NM$=$Non-majoritarian (mixed or proportional representation).} 
\footnotetext{\textbf{Dependent Variables:} ExpPC$=$Per capita expenditure, logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as a percentage of GDP.}\end{minipage}
\end{longtable}

@@

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)
export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators",
          format  = "latex")
```
\normalsize

A key methodological issue we had to address concerns the potential violation
of an important assumption in a meta-analysis, that of effect size independence
[@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
sample, authors frequently use similar datasets, and almost all papers fit more
than one model with similar variables, what suggests that the assumption does
not hold. We use two procedures to tackle this problem. First, we created two
sets of study coefficients to reduce the impact of multicollinearity in our
estimations. The first group includes only the most rigorous models from each
paper, that is, those estimated with the largest $n$, most control variables,
and fixed effects if the authors added them. If the article employed a
regression discontinuity design, we chose the coefficient from the optimal
bandwidth or from the intermediate one. This sample encompasses `r dim(dat)[1]`
estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed
two dependent or independent variables of interest\footnote{The papers that
used more than one dependent or independent variable of interest are
\citet{baqir1999districts, bjedov2014impact, bradbury2001legislative,
chen2007law, crowley2019law, erler2007termlimits, gilligan2001fiscal,
lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
ricciuti2003trading, ricciuti2004legislatures}.}. Our second sample, in
contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the 
`r length(unique(dat$id))` papers. Here we focus on the results for our restricted
sample as we consider them more robust, but the findings are very similar when
we use the extended set.

Our second procedure consists of employing multilevel random effect models
[@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
extra levels to the regular meta-analysis, one including a unique publication
ID for each paper, and another indicating the data source used in the original
study. By adding these two levels, we account for within- and between-study
variation, thus removing these sources of effect size dependency. More
information about the multilevel models can be found in Section H of the
Supplementary Material.

@@

Resumir resultados das meta-análises.
Incluir regressões com todos os coeficientes na tabela de meta-regressions.
Incluir frases com "highlights" na sub-seção de meta-regressions.
Trocar parágrafo introdutório e o de binomial z-tests pela nova versão do Danilo (que não subiu pro repo).

@@

We then proceed to the meta-analysis. We matched the house size variables with
our measures of government spending and created a theoretical $3 \times 3$
matrix. Out of the 9 possible variable combinations, we found only 7 in
the article pool. Our sample includes no papers that analyse the relationships
between the log lower chamber size and public expenditure per capita or between upper chamber size and the
logarithm of public expenditure per capita. We standardized effect sizes by drawing the coefficients and standard errors from the articles. When the latter were not directly available, we used t-statistics to retrieve them.

@@

Figure \ref{fig:plots} shows the forest plots for our restricted sample,
which includes only the `r dim(dat)[1]` main coefficients of the 
`r length(unique(dat$id))` selected papers. On the left side of the plots are 
the name of the study authors and the paper publication year. For unpublished
studies, we included the first year the paper was available online. The bars in
the middle show the reported effect sizes and the vertical lines indicate their
average, weighted by standard errors. The length of the lines represent the
precision of the estimates. The red line at the bottom of the figures displays
the aggregate coefficients plus their respective confidence intervals.

The first line of graphs reports the results for lower chamber size.
In the first model, which correlates lower chamber size and expenditure per capita, we find a
standardised mean difference (SMD) of `r round(mod[[1]]$TE.random,3)` and a standard error of `r round(mod[[1]]$seTE.random,3)`
(studies = `r mod[[1]]$k`, 95\% CI = [`r round(mod[[1]]$lower.random,3)`; `r round(mod[[1]]$upper.random,3)`], $p$-value = `r round(mod[[1]]$pval.random,3)` , prediction interval
= [`r round(mod[[1]]$lower.predict,3)`; `r round(mod[[1]]$upper.predict,3)`]). Therefore, we cannot reject the null hypothesis that the
effect size is zero. The $I^2$ statistic, which quantifies the degree of
heterogeneity among studies, is equal to `r round(mod[[1]]$I2*100, 2)`\%. $I^2$ values above 75\%
indicate very high study heterogeneity [@higgins2019cochrane].

We see similar results when we compare lower chamber size with log expenditure per capita. In
this model, the average effect size is `r round(mod[[3]]$TE.random,3)` and the standard error is
`r round(mod[[3]]$seTE.random,3)` (studies = `r mod[[3]]$k`, 95\% CI = [`r round(mod[[3]]$lower.random,3)`; `r round(mod[[3]]$upper.random,3)`], $p$-value = `r round(mod[[3]]$pval.random,3)`, prediction
interval = [`r round(mod[[3]]$lower.predict,3)`; `r round(mod[[3]]$upper.predict,3)`]; $I^2$ = `r round(mod[[3]]$I2*100, 2)`\%). The coefficient is 
statistically indistinguishable from zero.

In our restricted sample, larger lower house size also does not increase
government spending as a percentage of GDP (studies = `r mod[[5]]$k`, SMD = `r round(mod[[5]]$TE.random,3)`, SE =
`r round(mod[[5]]$seTE.random,3)`, 95\% CI = [`r round(mod[[5]]$lower.random,3)`; `r round(mod[[5]]$upper.random,3)`], $p$-value = `r round(mod[[5]]$pval.random,3)`, prediction interval =
[`r round(mod[[5]]$lower.predict,3)`; `r round(mod[[5]]$upper.predict,3)`], $I^2$ = `r round(mod[[5]]$I2*100, 2)`\%). In the extended sample the effect is negative, but it is also statistically insignificant.

>>>>

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity. Early
studies that empirically tested the "law of $1/n$", as the theory is currently
known, indeed found a positive correlation between the number of legislature
seats and different measures of government spending, although these first
results were mainly based on US state legislatures and the effect was often
limited to one house [e.g., @baqir2002districting; @gilligan1995deviations;
@gilligan2001fiscal].

Later research, however, has questioned the validity of the "law of $1/n$".
@primo2008distributive affirm that, due to spatial spillovers, a collection of
small districts can supply public goods more efficiently than the central
government. The authors conclude that a "reverse law of $1/n$" may hold,
wherein a higher number of legislators in small constituencies decrease the
overall public spending. Similarly, @primo2006stop and @chen2007law find that
lower and upper chambers may have mixed effects on government spending, while
@petterssonlidbom2012size argues that the impact of larger chamber sizes is
negative when using data from Finland and Sweden.

Since many empirical tests of the "law of $1/n$" have produced conflicting
results, scholars have expanded this research agenda and investigated how
institutional factors condition the original formulation of the theory. For
instance, authors such as @crowley2019law and @pecorino2018supermajority
accurately point out that collective action problems have been overlooked in
the literature, and recent findings indicate that bicameralism
[@maldonado2013legislatures], intergovernmental competition
[@crowley2015local], redistricting [@lee2018court], and party ideology
[@bjedov2014impact] strongly influence the relationship between seats and
spending. Moreover, the literature has increasingly applied causal inference
designs to estimate the effect of the "law of $1/n$", and in contrast to
previous studies using panel data, regression discontinuity designs generally
indicate that more legislators decrease public expenditures
[@debenedetto2018effect; @hohmann2017effect; @lewis2019legislature]. In this
respect, scholars have long been aware of the theoretical and empirical
limitations of the "law of $1/n$", and the proliferation of new studies reflect
a conscious attempt to assess the robustness of the theory [@crowley2019law].

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We select `r length(unique(dat$id))` articles that
use quantitative methods to evaluate the impact of legislature size over
government spending across several dimensions. Our study sample mirrors the
diversity of the literature. Out of the `r dim(dat)[1]` coefficients
included in our main analysis, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
negative and statistically significant. Meta-analysis provides a rigorous
approach to combine heterogeneous outcomes into a single estimation, and it
allows scholars to gain valuable insights from the aggregated data
[@cooper2019handbook; @hedges1985statistical]. Meta-analysis can also identify
potential sources of study variability, enabling researchers to assess threats
to external validity and direct future efforts into more promising areas of
academic inquiry [@doucouliagos2008democracy]. Research synthesis methods have
been successfully used in medicine and psychology since the 1970s
[@glass2015meta], and our work contributes to the burgeoning literature that
applies meta-analytic methods to understand challenging questions in political
science [@costa2017responsive; @doucouliagos2008democracy; @green2013field;
@lau2007effects; @schwarz2020supporting].

We run binomial tests and meta-regressions to further evaluate the relationship
between legislature size and government expenditures. We use the binomial tests
to asses whether the proportion of positive and negative coefficients in our
sample are statistically different from each other. In the meta-regressions, we
measure the effect of five moderators that capture different sources of
heterogeneity in the literature. As our sample includes both published and
unpublished articles, we also construct a series of funnel plots to test for
publication bias in existing research on the "law of $1/n$"
[@easterbrook1991publication; @gerber2001testing].

Aggregate results indicate that legislature size has no significant impact on
public spending. All of our main meta-analysis estimates show that the overall
effect is not statistically different from zero, thus confirming the
conflicting findings reported by the literature. However, when we look only at
articles that employ regression discontinuity designs (RDDs), we see that all
three papers included in our sample suggest that a higher number of legislators
leads to lower public spending [@debenedetto2018effect; @hohmann2017effect;
@lewis2019legislature]. In this regard, it is possible that methodological
choices explain part of the disparity observed in the literature, as studies
which use causal inference methods consistently point to the same direction.
One limitation of this finding is that these studies only test the impact of
lower house size on the natural logarithm of expenditure per capita, and it
remains unclear whether the results hold with other variables.

The meta-regressions provide additional evidence that our study sample is
highly heterogeneous and that effect sizes differ substantially according to
study specifications. When using our extended sample of `r dim(fulldat)[1]`
coefficients, we find that unicameralism is associated with higher public
spending, as predicted by the "law of $1/n$". Since most unicameral
legislatures are located in local governments (municipalities or districts),
this result supports the theory strictly in its first formulation. Moreover,
our meta-regressions indicate that larger upper chambers spend more in terms of
per capita expenditure than lower chambers, a result that also appears in the
binomial tests [@gilligan1995deviations; @gilligan2001fiscal]. Non-majoritarian
voting systems decrease government spending as a percentage of GDP, but they do
not have a relevant impact on the other measures of public expenditure,
following the idea that the $1/n$ effect grows weaker as the empirical cases
distance from the original definition of the law. Finally, meta-regression
results confirm that regression discontinuity models reduce public spending
estimates.

In summary, our results are in line with previous findings that lend partial
support to the law of $1/n$ [@chen2007law; @crowley2015local; @primo2006stop].
An assessment of the effects of collective action costs in these analyses is
crucial to determine the full mechanism operating behind these results.
Overall, our analysis does not provide robust support for the theory as
originally conceived.

# Data and Methods

We compiled our study sample in three search rounds. In the first round, we
gathered data from three large academic databases (Scopus, Microsoft Academic,
and Google Scholar) and looked for studies that were published in English and
cited \citet{weingast1981political}, as it is the foundational work in the
literature on the "law of $1/n$". To ensure that our sample was comparable, we
only selected papers that used quantitative methods to analyse
data\footnote{Since meta-analysis requires a single estimate per observation,
we excluded articles that use interaction terms or quadratic specifications of
our selected variables. Please refer to Section C in the Supplementary Material
for a detailed description of the selection procedure. We also included two
PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses)
flow diagrammes \citep{liberati2009prisma} showing the number of resulting
papers after each review step.}. After this stage, we identified six
measurements that the literature often employs to quantify government
expenditure and legislature size. For government expenditure, our study sample
uses (i) public expenditure as a share of GDP; (ii) public expenditure per
capita; and (iii) the natural logarithm of public expenditure per capita as its
main variables of interest. In regards to legislature size, the variables are
(i) lower chamber size; (ii) natural logarithm of lower chamber size; and (iii)
upper house size\footnote{There are a few important nuances concerning coding
of these variables. Unicameralism, for example, is captured both by lower
chamber size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of
the literature estimates how institutional designs affect this relationship,
ours and many other articles use both lower and upper chamber sizes as main
explanatory variables. We did not find any article that used the natural
logarithm of upper chamber size in their models.}.

In the second round, we did not require articles to cite @weingast1981political
and used a keyword-based query on Google Scholar to broaden the scope of the
first search. The search string contained terms strongly associated with the
literature on the "law of $1/n$" and was as follows: `("upper chamber size" OR
"lower chamber size" OR "council size" OR "parliament size" OR "legislature
size" OR "number of legislators" OR "legislative size") AND ("spending" OR
"expenditure" OR "government size")`. We again restricted the search to
articles written in English which employed quantitative methods. This search
added two new results to our sample [@coate2011government; @debenedetto2018effect], but neither of them included
variables beyond the six measures we had previously identified. In the third
search round, we looked into the personal webpages of every author whom we had
already included in our sample. The purpose of this manual search was to assess
whether there was any working paper or unpublished manuscript that we had
missed in the two former queries. All papers we found in the last search had
already been included in our sample. Combined, the three searches produced a
dataset of `r length(unique(dat$id))` studies as of the 10\textsuperscript{th}
of March 2021. Table \ref{tab:papers} contains the full list of articles we analyse in
this paper.

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead 
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Note:} Country codes
follow the ISO 3166-1 alpha-3 international standard.}
\footnotetext{\textbf{Journals:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
\footnotetext{\textbf{Methods:} 
OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
NM$=$Non-majoritarian (mixed or proportional representation).} 
\footnotetext{\textbf{Dependent Variables:} ExpPC$=$Per capita expenditure, logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as a percentage of GDP.}\end{minipage}
\end{longtable}

@@

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other coefficients", "Main sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)
export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive statistics of moderators",
          format  = "latex")
```
\normalsize

We also coded five moderators that may help us understand the heterogeneity in
the reported results. We included them in our meta-regressions alongside an
indicator for the type of independent variable used in the original study. The
additional moderators are: 1) publication year; 2) paper publication in an
academic journal; 3) estimation method; 4) institutional design; 5) electoral
system. Since the literature on the "law of $1/n$" is notably diverse, we
added only moderators that either refer to important theoretical questions,
such as the effect of the electoral system on public spending, or to essential
characteristics of the publications themselves. Although more moderators exist
in the literature (e.g., data aggregation level), they do not appear as often
as necessary for their inclusion in the meta-regressions. Table
\ref{tab:descriptive} shows the descriptive statistics of the moderator
variables.

A key methodological issue we had to address concerns the potential violation
of an important assumption in a meta-analysis, that of effect size independence
[@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
sample, authors frequently use similar datasets in their models,
and almost all papers fit more than one regression with similar variables, what
suggests that the assumption above does not hold. We use two procedures to tackle this
problem. First, we created two sets of study coefficients to reduce the impact
of multicollinearity in our estimations. The first group includes only the most
rigorous models from each paper, that is, those estimated with the largest $n$,
most control variables, and fixed effects if the authors added them. If the
article employed a regression discontinuity design, we chose the coefficient
from the optimal bandwidth or from the intermediate one. This sample
encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))`
articles analysed two dependent or independent variables of
interest\footnote{The papers that used more than one dependent or independent
variable of interest are \citet{baqir1999districts, bjedov2014impact,
bradbury2001legislative, chen2007law, crowley2019law, erler2007termlimits,
gilligan2001fiscal, lee2016supermajority, lee2018court,
maldonado2013legislatures, primo2006stop, ricciuti2003trading,
ricciuti2004legislatures}.}. Our second sample, in contrast, contains all the
`r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))`
papers. Here we focus on the results for our restricted sample as we consider
them more robust, but the findings are very similar when we use the extended
set.

Our second procedure consists of employing multilevel random effect models
[@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
extra levels to the regular meta-analysis, one including a unique publication
ID for each paper, and another indicating the data source used in the original
study. By adding these two levels, we account for within- and between-study
variation, thus removing these sources of effect size dependency and improving
the accuracy of the results. More information about the multilevel models can
be found in Section H of the Supplementary Material.

@@

@@

We then proceed to the meta-analysis. We matched the house size variables with
our measures of government spending and created a theoretical $3 \times 3$
matrix. Out of the 9 possible variable combinations, we found only 7 in
the article pool. Our sample does not contain any papers that analyse the relationships
between the log lower chamber size and public expenditure per capita, or between upper chamber size and the
logarithm of public expenditure per capita. We standardised effect sizes by drawing the coefficients and standard errors from the articles. When the latter were not directly available, we used t-statistics to retrieve them.

@@

Figure \ref{fig:plots} shows the forest plots for our restricted sample,
which includes only the `r dim(dat)[1]` main coefficients of the 
`r length(unique(dat$id))` selected papers.\footnote{Please refer to Sections H and I in the Supplementary Material for full results regarding both samples.} On the left side of the plots are 
the names of the study authors and paper publication year. For unpublished
studies, we included the first year the paper was available online. The bars in
the middle show the reported effect sizes and the vertical lines indicate their
average, weighted by standard errors. The length of the lines represent the
precision of the estimates. The red line at the bottom of the figures displays
the aggregate coefficients plus their respective confidence intervals.

The first line of graphs reports the results for lower chamber size. 
In the first model, which correlates lower house and expenditure per capita, we find a
standardised mean difference (SMD) of 0.022 and a standard error of 0.131
(studies = `r mod[[1]]$k`, 95\% CI = [-0.256; 0.299], $p$-value = 0.87). In the restricted sample, the effect of lower chamber size on the other two dependent variables is negative, but the remaining statistics are very similar. When we compare lower chamber size with log expenditure per capita, the average effect size is -0.031 and the standard error is
0.049 (studies = `r mod[[3]]$k`, 95\% CI = [-0.188; 0.127], $p$-value = 0.58). Larger lower house size also does not increase government spending as a percentage of GDP (studies = `r mod[[5]]$k`, SMD =
- 0.006, 95\% CI = [-0.0334; 0.021], $p$-value = 0.563). In the extended sample, the effect of lower house size on per capita expenditure and spending as a share of the GDP is positive, but the relationship with the logarithm of per capita expenditure is negative. In all cases, coefficients are statistically indistinguishable from zero.

Next, we present the meta-analyses using the logarithm of lower house
size. The relationship between this variable and the log of per capita expenditure is positive, but the coefficient is not significant
(studies = `r mod[[4]]$k`, SMD = 0.078, SE = 0.109, 95\% CI = [-0.225; 0.381], $p$-value =
0.515. The effect of log lower house size on expenditure as a percentage of the GDP is very similar, although the SMD is negative (studies =
`r mod[[6]]$k`, SMD = `r round(mod[[6]]$TE.random,3)`, SE = `r round(mod[[6]]$seTE.random,3)`, 95\% CI = [`r round(mod[[6]]$lower.random,3)`; `r round(mod[[6]]$upper.random,3)`], $p$-value = `r round(mod[[6]]$pval.random,3)`). Results in the full sample are also null, and the coefficients for each dependent variable have the same sign as the restricted sample -- positive and negative, respectively.

The third set of models uses upper house size as the main independent
variable. We find a positive correlation between this variable and expenditure per capita (studies = `r mod[[2]]$k`, SMD = 3.658, SE
= 4.299, 95\% CI = [-6.255; 13.572], $p$-value = 0.419), and a negative relationship with government spending as a percentage of GDP (studies = `r mod[[7]]$k`, SMD = `r round(mod[[7]]$TE.random,3)`, SE = `r round(mod[[7]]$seTE.random,3)`, 95\% CI
= [`r round(mod[[7]]$lower.random,3)`; `r round(mod[[7]]$upper.random,3)`], $p$-value = `r round(mod[[7]]$pval.random,3)`). Neither coefficients are significant. Results are very similar in the extended sample.
